##DV Project 1

1) I created a dataframe from the titanic database

```{r}
source("../01 Data/Titanic Analysis.R", echo = TRUE)
```

2) I created an interesting plot using the data in the dataframe


3) I created the first plot

```{r}
source("../02 Visualizations/Plot1.R", echo = TRUE)
```

This plot shows how the distribution of the fare the patrons had to pay to get on the Titanic based on there age and sex.

4) I created the second plot

```{r}
source("../02 Visualizations/Plot2.R", echo= TRUE)
```

This plot shows the same information as the previous plot, but does not include on the patrons that has sex as "NULL"

5) I created the third plot

```{r}
source("../02 Visualizations/Plot3.R", echo= TRUE)
```

This shows the amount the patrons had to pay based on sex and whether they did or did not survive.

6) created the fourth plot

```{r}
source("../02 Visualizations/Plot4.R", echo= TRUE)
```

This graph shows the same information as the previous graph, but breaksdown the patrons based on which class they were in as well.

7) created the fifth plot

```{r}
source("../02 Visualizations/Plot5.R", echo= TRUE)
```

This graph shows the information as the previous graph, but only for kids age 10 or younger